CDAM'25 examples

### 2025-10-17 Code/R/Research/HOSVD parameters estimate.Rmd
CDAM comments fixes 2
More mv cases

setwd(rprojroot::find_rstudio_root_file())
knitr::opts_knit$set(root.dir = getwd())
source(file = "./Research/TSSA.R")
```

@@

@@

save(
  rec.mssa.rmse,
  rec.tmssa.rmse,
  file = paste0("./Research/comp_results/mv_L_rmse", plot.name, ".RData")
)
```

>>>>

setwd(rprojroot::find_rstudio_root_file())
knitr::opts_knit$set(root.dir = getwd())
source(file = "./Source/TSSA.R")
```

@@

groups <- list(1:2)
groups3 <- list(1)
max.r <- max(sapply(groups, max))

@@

# save(
#   rec.mssa.rmse,
#   rec.tmssa.rmse,
#   file = paste0("./Research/comp_results/mv_L_rmse", plot.name, ".RData")
# )
```

### 2025-10-17 Code/R/Research/cases_research.Rmd
More mv cases

```{r}
setwd(rprojroot::find_rstudio_root_file())
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

@@

# equal amplitudes
A <- matrix(c(1, 1, 1, 1), ncol = P)
A_case <- "_ea"
# different amplitudes
# A <- matrix(c(1, 2, 1.5, 2.5), ncol = P)
# A_case <- "_da"

@@

```{r}
R <- 2

if (is.matrix(signal)) {
  ssa_err <- calc_errors_by_params(params_grid_ssa, R, pred_mssa_rec, rmse_ts_nd, signal, seed = 5)
  tssa_err <- calc_errors_by_params(params_grid_hossa, R, pred_homssa_rec, rmse_ts_nd, signal, seed = 5)
  save(ssa_err, tssa_err, file = paste0("./comp_results/cases_errors/two_periodics_mv", full_case, ".RData"))
} else {
  ssa_err <- calc_errors_by_params(params_grid_ssa, R, pred_ssa_rec, rmse_ts_nd, signal, seed = 5)
  tssa_err <- calc_errors_by_params(params_grid_hossa, R, pred_hossa_rec, rmse_ts_nd, signal, seed = 5)
  save(ssa_err, tssa_err, file = paste0("./comp_results/cases_errors/two_periodics", full_case, ".RData"))
}
```

@@

```{r}
print_errors(ssa_err)
summarise_errors(ssa_err)
```

```{r}
print_errors(tssa_err)
summarise_errors(tssa_err)
```

>>>>

```{r setup}
setwd(rprojroot::find_rstudio_root_file())
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

@@

# equal amplitudes
# A <- matrix(c(1, 1, 1, 1), ncol = P)
# A_case <- "_ea"
# different by summands amplitudes 
# A <- matrix(c(1, 2, 1, 2), ncol = P)
# A_case <- "_dsa"
# different by summands, proportional by ts amplitudes 
A <- matrix(c(1, 2, 3, 6), ncol = P)
A_case <- "_dspta"
# different amplitudes
# A <- matrix(c(1, 2, 1.5, 2.5), ncol = P)
# A_case <- "_da"

@@

```{r}
R <- 500

if (is.matrix(signal)) {
  ssa_err <- calc_errors_by_params(params_grid_ssa, R, pred_mssa_rec, rmse_ts_nd, signal, seed = 5)
  tssa_err <- calc_errors_by_params(params_grid_hossa, R, pred_homssa_rec, rmse_ts_nd, signal, seed = 5)
  save(ssa_err, tssa_err, file = paste0("./Research/comp_results/cases_errors/two_periodics_mv", full_case, ".RData"))
} else {
  ssa_err <- calc_errors_by_params(params_grid_ssa, R, pred_ssa_rec, rmse_ts_nd, signal, seed = 5)
  tssa_err <- calc_errors_by_params(params_grid_hossa, R, pred_hossa_rec, rmse_ts_nd, signal, seed = 5)
  save(ssa_err, tssa_err, file = paste0("./Research/comp_results/cases_errors/two_periodics", full_case, ".RData"))
}
```

@@

```{r}
# load()
```

```{r}
if (is.matrix(signal)) {
  print_errors_m(ssa_err)
} else {
  print_errors(ssa_err)
}
summarise_errors(ssa_err)
```

```{r}
if (is.matrix(signal)) {
  print_errors_m(tssa_err)
} else {
  print_errors(tssa_err)
}
summarise_errors(tssa_err)
```

### 2025-10-17 Code/R/Research/cdam25_examples.Rmd
More mv cases

groups <- list(1:2)
groups3 <- list(1:2)
max.r <- max(sapply(groups, max))

@@

@@

save(rec.summary, file = "./Research/comp_results/cdam25_2d_rec.RData")
xtable(
  rec.summary,
  digits = 3,
  display = c("s", "s", rep("f", 4)),
  align = rep("c", 6)
)
```

>>>>

groups <- list(1:2)
groups3 <- list(1)
max.r <- max(sapply(groups, max))

@@

# load("./Research/mv_coef/L_no_rates.RData")

@@

# save(rec.summary, file = "./Research/comp_results/cdam25_2d_rec.RData")
xtable(
  rec.summary,
  digits = 3,
  display = c("s", "s", rep("f", 4)),
  align = rep("c", 6)
)
```
